Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-10-07 GWLDCII.tex
a couple comments

\textbf{Case 2}: Suppose $p = (i, m)$, i.e. $p$ has an end on the $i^{th}$ edge. If no other propagators are supported on the vertex $i$ then the corresponding column of $C(W)$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction. \st{Since $I_i(p) = i$ there can be no propagator supported on $i$ with an end on the edge $(i-1, i)$.  Thus to have another propagator supported on $i$ there is at least one other propagator on edge $(i,i+1)$.  Further since since $I_i(p)=i$, one of these other propagators contributes $i+1$ in $I_i$, so we can take $q$ to be the propagator such that $I_i(q)=i+1$.  We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure {\ref{fig no big factors}}).}  \hlfix{Since $p$ is the first propagator in the ordering imposed by $I_i$, it is the counterclockwise most propagator supported on $i$ (by Remark {\ref{clockwise ordering rem}}). Since there are multiple propagators supported on $i$, there must be a $q$ ending on edge $i$, such that $I_i(q) = i+1$, that is second clockwisemost propagators supported by $i$.}{Alt. proof} Write $q = (i, j)$ for the support of $q$.  The situation for $q$ is very similar to case 1: \st{in particular, we have $I_{i+1}(q) = j$ by Lemma {\ref{vertex cyclic int lem}} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.}{\color{violet}if we have $r$ such that $I_i(r) = j$, as above, $r$ lies outside $q$: $r \in \cP_{out}(q, <_i)$. }

@@

\item \sanote{changed $b$ to $a+1$ here.} Suppose propagators $p$ and $q$ are supported on a common edge  $a$, with $I_i(p)=a$ and $I_i(q)=a+1$.  Let $x_{p,a},x_{p,a+1},x_{q,a},x_{q,a+1}$ be the associated variables in $C(W)$. For any fixed bijection $\sigma$ from $\cP\setminus\{p,q\}$ to $I_i \setminus\{a,a+1\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection from propagators to $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto a+1$ or $p\mapsto a+1$ and $q\mapsto a$.  The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $(x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a})$ \note{Could this use a ref back to where we discuss this kind of arugment in more detail.} with the minor coming from $\cP\setminus\{p, q\}$ and $I_i \setminus \{a,a+1\}$.  Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.  Therefore no such terms exist and $x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a}$ is a factor of $\Delta_{I_i}$.

>>>>

\textbf{Case 2}: Suppose $p = (i, m)$\note{Do we actually need $m$, if so perhaps should remove as muddies waters}, i.e. $p$ has an end on the $i^{th}$ edge. If no other propagators are supported on the vertex $i$ then the corresponding column of $C(W)$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction. \st{Since $I_i(p) = i$ there can be no propagator supported on $i$ with an end on the edge $(i-1, i)$.  Thus to have another propagator supported on $i$ there is at least one other propagator on edge $(i,i+1)$.  Further since since $I_i(p)=i$, one of these other propagators contributes $i+1$ in $I_i$, so we can take $q$ to be the propagator such that $I_i(q)=i+1$.  We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure {\ref{fig no big factors}}).}  \hlfix{Since $p$ is the first propagator in the ordering imposed by $I_i$, it is the counterclockwise most propagator supported on $i$ (by Remark {\ref{clockwise ordering rem}}). Since there are multiple propagators supported on $i$, there must be a $q$ ending on edge $i$, such that $I_i(q) = i+1$, that is second clockwisemost propagators supported by $i$.}{Alt. proof} Write $q = (i, j)$ for the support of $q$.  The situation for $q$ is very similar to case 1: \st{in particular, we have $I_{i+1}(q) = j$ by Lemma {\ref{vertex cyclic int lem}} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.}{\color{violet}if we have $r$ such that $I_i(r) = j$, as above, $r$ lies outside $q$: $r \in \cP_{out}(q, <_i)$. }

@@

\item \sanote{changed $b$ to $a+1$ here.} Suppose propagators $p$ and $q$ are supported on a common edge  $a$, with $I_i(p)=a$ and $I_i(q)=a+1$.  Let $x_{p,a},x_{p,a+1},x_{q,a},x_{q,a+1}$ be the associated variables in $C(W)$. For any fixed bijection $\sigma$ from $\cP\setminus\{p,q\}$ to $I_i \setminus\{a,a+1\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection from propagators to $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto a+1$ or $p\mapsto a+1$ and $q\mapsto a$.  The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of $(x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a})$ \note{Could this use a ref back to where we discuss this kind of arugment in more detail.} with the minor coming from $\cP\setminus\{p, q\}$ and $I_i \setminus \{a,a+1\}$.  Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part\note{let's talk about this}.  Therefore no such terms exist and $x_{p,a}x_{q,a+1}-x_{p,a+1}x_{q,a}$ is a factor of $\Delta_{I_i}$.
